---
title: "Prediction Assignment Writeup"
author: "Zhichao HAN"
date: "02/20/2015"
output: html_document
---

## Introduction

This is a report for pratical machine learning course.

## Data Preprocess

```{r}
library(caret)
set.seed(1024)

data.train <- read.csv("data/pml-training.csv", stringsAsFactors=FALSE)
data.train$classe <- as.factor(data.train$classe)
data.train <- data.train[,-nearZeroVar(data.train)]
data.train <- data.train[,-c(1,2,3,4,5,6,7)]
```

The training data has been loaded. Some unrelavent features have been removed from ``data.train``.

```{r}
inTrain <- createDataPartition(y=data.train$classe, p=0.6, list=FALSE)
data.valid <- data.train[-inTrain,]
data.train <- data.train[inTrain,]
```

The dataset has been splitted into train-set and valid-set.

```{r}

preObj <- preProcess(data.train[,-length(data.train)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.80)
data.train.transformed <- predict(preObj,data.train[,-length(data.train)])
data.valid.transformed <- predict(preObj,data.valid[,-length(data.valid)])
```

The missing data has been filled by knn-impute method and the dimension has been reduced via PCA. Both the train-set and the valid-set have been transformed.

## Training and Predicting

```{r}
modelFit <- train(data.train$classe ~.,data=data.train.transformed, method='rf', ntree=10)
y.valid <- predict(modelFit, data.valid.transformed)
confusionMatrix(data.valid$classe, y.valid)
```

RandomForest - ``rf`` has been used as the model to train and the accuracy on the validating dataset is around 90%.

```{r}
data.test <- read.csv("data/pml-testing.csv", stringsAsFactors=FALSE)
data.test <- data.test[,names(data.test) %in% names(data.train)]

data.test.transformed <- predict(preObj, data.test)
y.test <- predict(modelFit, data.test.transformed)
```
